### 2015-11-03 CVPR16/Source/experiments.tex
Added continous bouding box energy. Moved all other energies to the supplementary material. Moved the qualitative results from localization experiment to supplementary material as well.

\subsection{Localization Experiment}
To prove the effectiveness of our method we apply it to the localization
problem. We estimate the position, orientation and dimensions of the car with
our framework and compute the error in birds eye view domain along the ground
plane. We report error in three metrics translation error (t) in meters per
car, yaw error (yaw) in radians per car and dimension error is again meters per
car.

@@

\subsubsection{Point tracks energy with occlusion}
\label{sec:totalContPtTracksEnergy}
We model continuous point tracks energy with explicit occlusion reasoning as
the expected re-projection error over the association probability,

@@

\subsubsection{Object detection energy}

We model object detection energy as the norm of difference in the coordinates
of the projected bounding box and detected bounding box. The detected bounding
box is represented by the extrema along X and Y dimensions $\bb{i} = [\xmin,
\ymin, \xmax, \ymax]^\top$. If $\dimsn{i} = [l, w, h]^\top$ represent the 3D
then we can compute the eight corners of the cuboid model in the tracklet
coordinate transform as

With slight abuse of notation for projection operator we write this energy as
\begin{align}
  \EnergyBBox &= \left\| \projectionOf{\dimsn{i}} - \bb{i}\right\|^2_2 \enspace.
\end{align}

@@

\subsubsection{Lane energy}
\label{sec:laneEnergy}
 The lanes are modeled as splines. Here we assume that the confidence in lane
 detection is decreases as the distance from the lane center increases.  The
 energy is given by the dot product between car orientation and tangent to the
 lane at that point.

\begin{align}
  \label{eq:laneOrientationEnergy}
  \Energy{lane} = 
  \sum_{m \in M_{\text{close}}}
  (1 - \ori{i}{t} \cdot \text{TAN}(L_{m}(k), \pos{i}{t}) )
\LaneUncertainty{\pos{i}{t}}
\end{align}
where $M_{\text{close}} = \{m : \text{DIST}(L_{m}(k), \pos{i}{t}) < d_{\text{thresh}}\} $ is
the set of nearby lanes close to the object by a certain distance threshold $d_{\text{thresh}}$ and 
\begin{align}
\LaneUncertainty{\pos{i}{t}} = 
  \frac{1}{1 + \exp(-q(w_{\text{road}} - \text{DIST}(L_{m}(k), \pos{i}{t})))}
\end{align}
for some constant $w_{\text{road}}$ that represents the width of the road.

\subsubsection{Transition probability}
Dynamics constraints should not only enforce smooth trajectories, but also the
holonomic constraints.  The following energy adds a penalty if the change in
position is not in direction of previous orientation.

\begin{align}
  \label{eq:totalPosTransitionEnergy}
  \Energy{dyn-hol} = 1 - \ori{i}{t-1} \cdot (\pos{i}{t} - \pos{i}{t-1})
\end{align}

The following energy adds a penalty for change in position and orientation
but a penalty for change in velocity is much better approximation. However, in
a Markovian setting that would mean extending the state space of the car to
include velocity.

\begin{align}
  \Energy{dyn-ori} &= \|\ori{i}{t} - \ori{i}{t-1}\|^2\\
  \Energy{dyn-vel} &= \|(\pos{i}{t} - 2\pos{i}{t-1}) + \pos{i}{t-2}\|^2
\end{align}

As a result the dynamics are modeled by weighted combination of holonomic
constraint and smoothness constraints.

\begin{align}
  \WEnergy{dyn} &= \WEnergy{dyn-hol} + \WEnergy{dyn-ori} + \WEnergy{dyn-vel}
\end{align}

\subsubsection{Size Prior}

Prior can include among many other things the size prior on the car.

\begin{align}
  \label{eq:totalSizeEnergy}
  \Energy{size} &= (\dimsn{i} - \expDimsn)^\top\Sigma_{\expDimsn}^{-1}(\dimsn{i} -
  \expDimsn)
\end{align}

where $\expDimsn$ is the mean TP dimensions and
$\Sigma_{\expDimsn}$ is the correspondence covariance matrix.

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{results/0009_contPtTracks_size_bboxOcc_yawTstepWiseInference_0000000061.png}
\end{figure}
\begin{figure}
  \includegraphics[width=\columnwidth]{results/0009_lane_size_bboxOcc_yawTstepWiseInference_0000000061.png}
\end{figure}

\begin{table}
  \centering
  \begin{tabular}{lrrr}
    \toprule
    Energy & t & yaw & dim \\
    \midrule
    initialization                                                                                  & 3.79 & \textbf{0.86} & 1.64 \\
    $\EnergyLane+\EnergySize+\EnergyBBox+\EnergyDyn                                       $ & 3.83 & 0.90 & \textbf{1.14} \\
    %$\EnergyLane+\EnergySize+\EnergyBBoxocc+\EnergyDyn                                    $ & 3.83 & 0.90 & 1.14 \\
    %$\EnergyLane+\EnergySize+\EnergyBBoxocc+\EnergyDyn+\EnergyCol                         $ & 3.92 & 0.91 & 1.15 \\
    %$\EnergyLane+\EnergyContpttracks+\EnergySize+\EnergyBBoxocc+\EnergyDyn             $ & 3.81 & 0.92 & 1.59 \\
    % \EnergyBBox+\EnergyDyn+\EnergyCol $
    $\EnergyTrackNoOcc+\EnergyCol + \EnergyLane + \dots$  & 3.80 & 0.91 & 1.58 \\
    $\EnergyTrack+\EnergyCol + \EnergyLane + \dots$ & \textbf{3.78} & 0.91 & 1.58 \\
    \bottomrule
  \end{tabular}
  \caption{Localization experiment results with different combination of energies. We report error in three metrics translation error (t) in meters per car, yaw error (yaw) in radians per car and dimension error is again meters per car.}
\end{table}

>>>>

\subsection{Localization Experiment}
To show the effectiveness of our method we apply it to the localization
problem. We estimate the position, orientation and dimensions of the car with
our framework and compute the error in birds eye view domain along the ground
plane. We report error in three metrics translation error (t) in meters per
car, yaw error (yaw) in radians per car and dimension error is again meters per
car. The results are shown in Table~\ref{tab:localizationExperiment}.

@@

\subsubsection{Continuous point tracks energy with occlusion}
\label{sec:totalContPtTracksEnergy}
We model continuous point tracks energy with explicit occlusion reasoning as
the expected re-projection error over the association probability,

@@

\subsubsection{Continuous bounding box energy with occlusion}

Object detection is usually followed by non-maximal suppression that results in
discarding similar bounding boxes. When we are jointly optimizing detections
with other cues, it is not usually desirable to go with a single bounding box.
Hence, we keep all the bounding box detections by approximating them with
multi-modal sum of Gaussian like logistic functions. We fit the parametric function of the form 
%
\begin{multline}
  S(\bb{i}) = \\
  \sum_k A_k \exp(-(\bb{i}-\mu^{(d)}_k)^\top \Sigma^{(d)-1}_k
  (\bb{i}-\mu^{(d)}_k))
\end{multline}
%
to detection scores, by non-linear error minimization with initialization from
non-maximal suppressed outputs. Here $\mu^{(d)}_j$ is one of the $k$ modes as a
4D vector representing a single bounding box as $[\minx, \miny, \maxx,
\maxy]^\top$. The optimization is constrained with symmetry and positive
definiteness of $\Sigma^{(d)-1}_k$, $\maxx \ge \minx$ and $\maxy \ge \miny$.

\paragraph{Detection scores with occlusion reasoning} 
\def\u{\mathbf{u}}
With our model of $\Ptrans$ described in Section \ref{sec:ptransmission}, we can
compute the probability of a point $\u$ on image be occluded assuming
the point is on traffic participant (TP) $i$ with mean depth $\mu^{(i)}_d$ as
\begin{align}
  O_{i}(\u, \mu^{(i)}_d) = 1 - \Ptransmission(\mu^{(i)}_d\u) \enspace .
\end{align}

If we know a portion of our proposed detection bounding box is known to be
occluded, then we would like to decrease the confidence in the detection score
about the localization of that end of the object. Assuming that the occlusion
is often on the boundary of detection bounding boxes, we want to decrease our
confidence on the mean detection boundaries around the occluded boundaries.
To re-model our detection scores scaled by continuous occlusion we sample
$O_{i}(\mathbf{u}, \mu^{(i)}_d)$ at the hypothesized detection boundaries from
GMM $S(.)$ and we augment the detection boundary covariance matrix by
$\mathcal{P}_{j} = \rho_{j}\rho_{j}^\top$ where $\rho_{j} = O_{j}(\mathbf{u},
\mu^{(i)}_d)$. The new covariance matrix in detection score is given by 
  $\Sigma'^{(d)}_j = \mathcal{P}_{j} + \Sigma^{(d)}_j$.
The detection scores GMM with occlusion is given by replacing the covariance
matrix
%
\begin{multline}
  S'(\bb{i}) =
  \\
  \sum_j A_j \exp(-(\bb{i}-\mu^{(d)}_j)^\top \Sigma'^{(d)-1}_j
  (\bb{i}-\mu^{(d)}_j))
\end{multline}

The energy of detection scores is simply take to be the inverse of the detection score.
\begin{align}
  \Energy{detect}(\{ \relp{i}{t} \}_i, \{ \relp{i}{t-1} \}_i, \{\dimsn{i}\}_i ) = \frac{1}{S'(\bb{i})}
\end{align}

@@

\subsubsection{Other energies}
Other energies we use are described in detail in the supplementary material. We briefly describe them here:
\begin{description}
  \item[Lane energy ($\Energy{lane}$)] This energy term constrains the
    orientation of traffic participants to be parallel to the nearest detected
    lane. The lanes are either detected visually or obtained from GPS and Map 
    information.
  \item[Transition probability ($\Energy{dyn}$)] We use these energies to
    constrain the motion of cars to be smooth in linear motion and rotation
    motion. We also constrain cars to move in the direction of heading.
  \item[Size prior ($\EnergySize$)] We use size prior of cars by using the mean
    of cars over the KITTI dataset.
\end{description}

@@

\begin{table}
  \centering
  \begin{tabular}{lrrr}
    \toprule
    Energy & t & yaw & dim \\
    \midrule
    initialization                                                                                  & 3.79 & \textbf{0.86} & 1.64 \\
    $\EnergyLane+\EnergySize+\EnergyBBox+\EnergyDyn                                       $ & 3.83 & 0.90 & \textbf{1.14} \\
    %$\EnergyLane+\EnergySize+\EnergyBBoxocc+\EnergyDyn                                    $ & 3.83 & 0.90 & 1.14 \\
    %$\EnergyLane+\EnergySize+\EnergyBBoxocc+\EnergyDyn+\EnergyCol                         $ & 3.92 & 0.91 & 1.15 \\
    %$\EnergyLane+\EnergyContpttracks+\EnergySize+\EnergyBBoxocc+\EnergyDyn             $ & 3.81 & 0.92 & 1.59 \\
    % \EnergyBBox+\EnergyDyn+\EnergyCol $
    $\EnergyTrackNoOcc+\EnergyCol + \EnergyLane + \dots$  & 3.80 & 0.91 & 1.58 \\
    $\EnergyTrack+\EnergyCol + \EnergyLane + \dots$ & \textbf{3.78} & 0.91 & 1.58 \\
    \bottomrule
  \end{tabular}
  \caption{Localization experiment results with different combination of energies. We report error in three metrics translation error (t) in meters per car, yaw error (yaw) in radians per car and dimension error is again meters per car.}
  \label{tab:localizationExperiment}
\end{table}
